VOCC outline

### 2020-04-24 ms/ms.Rmd
Start editing

---
title: VOCC outline
author: |
  Philina A. English^1^, Authors, ...\
  ^1^Pacific Biological Station, Fisheries and Oceans Canada,\
     3190 Hammond Bay Road, Nanaimo, BC, V6T 6N7, Canada;\
     philina.english@dfo-mpo.gc.ca\
output:
  bookdown::pdf_document2:
    number_sections: yes
    toc: no
fontfamily: libertine
fontsize: 12pt
header-includes:
  - \usepackage{setspace}
  - \onehalfspacing
  - \usepackage{lineno}
  - \usepackage{fullpage}
  - \usepackage{pdflscape}
  - \linenumbers
  - \modulolinenumbers[2]
geometry: "left=2.64cm, right=2.64cm, top=2.54cm, bottom=2.54cm"
bibliography: "refs.bib"
csl: "ecology.csl"
---

```{r setup, echo=FALSE, cache=FALSE, message=FALSE, results='hide', warning=FALSE}
library(knitr)
library(here)
opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  autodep = TRUE,
  fig.align = "center",
  fig.pos = "htb"
)

# TODO: is this where this should go?
alldata <- readRDS(paste0("../analysis/VOCC/data/all-do-with-null-1-untrimmed-allvars.rds"))
model <- readRDS("../analysis/VOCC/data/trend-all-95-all-do-04-11-trend-with-do-family-family-1-500.rds")
```

# Abstract {-}

# **Introduction**

@@

# **Methods**

@@

## *Survey data*

We analyze abundance, distribution, and morphometric data for 36 species of Pacific groundfish most regularly encountered on fisheries-independent bottom trawl surveys and relatively widely distributed within Canadian waters. 
Surveys are stratified within four separate regions two of which are surveyed each year since 2005 (with surveys also conducted in some regions in 2003 & 2004): Hecate Strait and Queen Charlotte Sound (odd years) and West Coast Vancouver Island and West Coast Haida Gwaii (even years). 
Each region is sampled over the same month long period between late May and early August each year.
Combined these surveys cover most of the upper continental slope and shelf in Canada and share the same random depth stratified design, fishing gear, and fishing protocols (TODO: Sinclair et al. 2003).
Only successful tows of 15--20 min duration are included in analyses and total biomass of each species captured was converted to a biomass density estimate based on the speed, distance covered and net opening.
Catches of between 10--50 individuals are weighed and measured individually, while larger catches are subsampled and for commercially important species data on maturity and age are also collected.

## *Estimate spatiotemporal variation in adult and immature biomass densities*

Because ontogenetic shifts in habitat, particularly depth, are well documented in groundfish species [@mindel2016; @barbeaux2018; @li2019], we estimate biomass densities separately for mature and immature size classes whenever possible (maturity is not assessed for certain Chondrichthians, or when catches are particularly low).
To do this, we first estimate length at 50% maturity (defined by gonadal development stages of immature or maturing vs. mature, ripe, or spent) using ogives fit as sex-specific logistic regressions to individual specimens.
When sufficient samples were available in all years, a random effect of year was included to allow for temporal change in size at maturity (TODO: REF) and these year specific thresholds were used to split observed catches.
For those species lacking maturity data in some years, a random effect of tow id was included instead, but catches were split based on the global estimate.
For all catches exceeding the species-specific threshold count of individual fish, either a random subset of roughly 50 fish, or all individuals will be measured for both length and weight (occasional missing weights were estimated from $\log(W_i) \sim \mathrm{Student-t} (df = 3, \log(a) + b \log(L_i), \sigma)$, with $W_i$ and $L_i$ representing the weight and length for fish $i$ and $\sigma$ representing the observation error scale).
We then calculate the summed weight of all measured which exceeded the length at 50% maturity threshold, divided by the total weight of all measured fish, and multiply this ratio by the estimated biomass density for each tow.
For each tow which resulted in a catch too small for detailed measurements to have been taken, we apply the mean ratio from all measured tows to estimate mature biomass.
Immature density was estimated as the difference between the total density and mature density.

@@

## *Estimate climate velocities*

@@

## *Link biomass change with climate*

@@

# **Results**

>>>>

---
title: VOCC outline
author: |
  Philina A. English^1^, Authors, ...\
  ^1^Pacific Biological Station, Fisheries and Oceans Canada,\
     3190 Hammond Bay Road, Nanaimo, BC, V6T 6N7, Canada;\
     philina.english@dfo-mpo.gc.ca\
output:
  bookdown::pdf_document2:
    number_sections: no
    toc: no
fontfamily: libertine
fontsize: 12pt
header-includes:
  - \usepackage{setspace}
#  - \onehalfspacing
  - \usepackage{lineno}
  - \usepackage{fullpage}
  - \usepackage{pdflscape}
#  - \linenumbers
#  - \modulolinenumbers[2]
abstract: TODO
geometry: "left=2.64cm, right=2.64cm, top=2.54cm, bottom=2.54cm"
bibliography: "refs.bib"
csl: "ecology.csl"
---

```{r setup, echo=FALSE, cache=FALSE, message=FALSE, results='hide', warning=FALSE}
library(knitr)
library(here)
opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  autodep = TRUE,
  fig.align = "center",
  fig.pos = "htb"
)
```

```{r data, cache=TRUE}
alldata <- readRDS(paste0("../analysis/VOCC/data/all-do-with-null-1-untrimmed-allvars.rds"))
model <- readRDS("../analysis/VOCC/data/trend-all-95-all-do-04-11-trend-with-do-family-family-1-500.rds")
```

# Introduction

@@

# Methods

@@

## Survey data

We analyze abundance, distribution, and morphometric data for 36 species of Pacific groundfish that are regularly encountered on fisheries-independent bottom trawl surveys and widely distributed within western Canadian waters. 
The surveys are stratified within four regions, two of which are generally surveyed each year since 2003: Hecate Strait and Queen Charlotte Sound (odd years) and West Coast Vancouver Island and West Coast Haida Gwaii (even years). 
Each region is sampled over the same month-long period between late May and early August each year.
Combined, these surveys cover most of the upper continental slope and shelf in western Canada and share the same random depth-stratified design, fishing gear, and fishing protocols (TODO: Sinclair et al. 2003).
We only include successful tows of 15--20 min duration in analyses and convert total biomass of each species to a biomass density based on the speed, distance covered, and net opening.
Catches of between 10--50 individuals are weighed and measured individually, while larger catches are subsampled and, for commercially important species, data on maturity and age are collected.

## Estimate spatiotemporal variation in adult and immature biomass densities

Because ontogenetic shifts in habitat, particularly depth, are well documented in groundfish species [e.g., @mindel2016; @barbeaux2018; @li2019], we estimate biomass densities separately for mature and immature size classes whenever possible (maturity is not assessed for certain Chondrichthians, or when catches are particularly low).
To do this, we first estimate length at 50% maturity (defined by gonadal development stages of immature or maturing vs. mature, ripe, or spent) using ogives fit as sex-specific logistic regressions to individual specimens.
When sufficient samples were available in all years, a random effect of year was included to allow for temporal change in size at maturity (TODO: REF) and these year specific thresholds were used to split observed catches.
For those species lacking maturity data in some years, a random effect of tow id was included instead, but catches were split based on the global estimate.
For all catches exceeding the species-specific threshold count of individual fish, either a random subset of roughly 50 fish, or all individuals will be measured for both length and weight (occasional missing weights were estimated from $\log(W_i) \sim \mathrm{Student-t} (df = 3, \log(a) + b \log(L_i), \sigma)$, with $W_i$ and $L_i$ representing the weight and length for fish $i$ and $\sigma$ representing the observation error scale).
We then calculate the summed weight of all measured which exceeded the length at 50% maturity threshold, divided by the total weight of all measured fish, and multiply this ratio by the estimated biomass density for each tow.
For each tow which resulted in a catch too small for detailed measurements to have been taken, we apply the mean ratio from all measured tows to estimate mature biomass.
Immature density was estimated as the difference between the total density and mature density.

@@

## Estimate climate velocities

@@

## Link biomass change with climate

@@

# Results
